Nested sampling with two objective functions

### 2016-02-06 Paper/ms.tex
Image model

>>>>

The unknown parameters are a set of pixel intensities
$\{m_i\}_{i=1}^n$ where $n$ is the number of pixels and $m_i \geq 0$.
The dataset is also a collection of pixel intensities $\{D_i\}_{i=1}^n$.
The prior for the dataset given the parameters is a normal distribution
with mean given by the underlying image $\{m_i\}$ convolved by
a point spread function. The standard deviation of each pixel is
$\sigma$, assumed known. This is usually written as

\begin{eqnarray}
\boldsymbol{D} = \boldsymbol{P}\boldsymbol{m} + \boldsymbol{n}
\end{eqnarray}
where $\boldsymbol{n}$ is the noise in each pixel and $\boldsymbol{P}$ is
the blurring operator written in matrix form.
